Scipion Tailored for TEM Facilities: Image Processing in Streaming

### 2018-02-28 3.workflow_scilifelab.tex
Update 3.workflow_scilifelab.tex

The facilities can be accessed by Swedish researchers through a peer-reviewed routine. Applications can be 
submitted through an Application Portal (reference???) and will be evaluated once every three months based on their 
scientific merit and technical feasibility by a national Project Evaluation Committee. On the other side, 
some time of the facility is reserved for internal research groups at Stockholm University. Internally, the allocation
of the microscope (and other instruments) time is managed by a Booking System (reference???).

At the beginning of 2016, the Cryo-EM facility at SciLifeLab became one of the early adopters of Scipion 
for on the fly data processing. Before, there were some home-made scripts to perform motion correction (with motioncor)
and CTF estimation (with Gctf). The microscope operators recognized the importance of  
a more general framework with the possibility to be extended with new programs. Another strong point was the 
the availability of graphical tools for data analysis and quick feedback about the data collection. Initially, the 
same setup script from the CNB was used, but it had some limitations for this more complex setup with more 
requirements. In the following sections we will briefly describe the computational infrastructure at the
SciLifeLab node and the implementation of a Session Wizard to automate the initial setup while fetching 
information from other sources external to Scipion.

\subsubsection{Infrastructure}

@@

The initial attempt to ease the setup of Scipion projects for stream processing was based  
on the original script developed at the CNB. But it was difficult to reuse the existing code due to a different folder
structure and, more important, a different logic about users and microscopes management. To address the new set
of requirements, a new ``wizard'' is being developed at SciLifeLab and can be found in the following open source repository: 
\url{https://github.com/delarosatrevin/scipion-session}

>>>>

The facilities can be accessed by Swedish researchers through a peer-reviewed routine. Applications can be 
submitted through an Application Portal [**reference???] and will be evaluated once every three months based on their 
scientific merit and technical feasibility by a national Project Evaluation Committee. On the other side, 
some time of the facility is reserved for internal research groups at Stockholm University. Internally, the allocation
of the microscope (and other instruments) time is managed by a Booking System [** name of the booking system and reference???].

At the beginning of 2016, the Cryo-EM facility at SciLifeLab became one of the early adopters of \scipion 
for on the fly data processing. Before, there were some home-made scripts to perform motion correction (with motioncor)
and CTF estimation (with Gctf). The microscope operators recognized the importance of  
a more general framework with the possibility to be extended with new programs. Another strong point was the 
the availability of graphical tools for data analysis and quick feedback about the data collection. Initially, the 
same setup script from the CNB was used, but it had some limitations for this more complex setup with more 
requirements. In the following sections we will briefly describe the computational infrastructure at the
SciLifeLab node and the implementation of a Session Wizard to automate the initial setup while fetching 
information from other sources external to Scipion.

\subsubsection{Infrastructure}
[** to be done]

@@

The initial attempt to ease the setup of \scipion projects for stream processing was based  
on the original script developed at the CNB. But it was difficult to reuse the existing code due to a different folder
structure and, more important, a different logic about users and microscopes management. To address the new set
of requirements, a new ``wizard'' is being developed at SciLifeLab and can be found in the following open source repository: 
\url{https://github.com/delarosatrevin/scipion-session}
